\documentclass[11pt]{article}

% Use Helvetica font.
%\usepackage{helvet}

%\usepackage[T1]{fontenc}
%\usepackage[sc]{mathpazo}
\usepackage{color}
\usepackage{amsmath,amsthm,amssymb,multirow,paralist}
%\renewcommand{\familydefault}{\sfdefault}

% Use 1/2-inch margins.
\usepackage[margin=0.8in]{geometry}
\usepackage{hyperref}

\begin{document}

\begin{center}
{\Large \textbf{Project Proposal}}\\
\end{center}

\linethickness{1mm}\line(1,0){498}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Project Title}

Handwritten signature verification system with Siamese neural networks.

\section{Team Members}

\begin{itemize}
  \item Lucas Sorge
  \item Kenny Jia Hui Leong
\end{itemize}

\section{Project Details}

\subsection{Project Objective}

Please describe your project objective in this part.

\begin{itemize}
  \item What is the project Objective?
  \begin{itemize}
      To develop a system that verifies handwritten signatures with only one reference sample.
  \end{itemize}
  \item What problem to solve?
  \begin{itemize}
      To prevent signature forgery which is common in banking, legal and financial activities.
  \end{itemize}
  \item Why the problem is important?
  \begin{itemize}
      Many authentication systems still rely on signatures and traditional Machine Learning(ML) models require large labeled datasets.
  \end{itemize}
  \item Why machine learning can help to solve the problem?
  \begin{itemize}
      Siamese neural networks can compare a new signature against a stored reference with high accuracy, even if only one sample is available (Koch et al., 2015).
  \end{itemize}
\end{itemize}

\subsection{Datasets}

Please describe your dataset in this section.

\begin{itemize}
  \item What is the data and where you obtain it?
  \begin{itemize}
      Pashkin, Zack. Image dataset for handwritten signature verification. Kaggle.\\
      https://www.kaggle.com/datasets/tienen/handwritten-signature-verification/data
  \end{itemize}
  \item How the data is collected?
  \begin{itemize}
      Crowdsourcing.
  \end{itemize}
  \item What will be the features and labels you will use?
  \begin{itemize}
      Features: Original unique IDs, original signatures, forged unique IDs, forged signatures.\\
      Labels: Original signature, forged signature.
  \end{itemize}
  \item How many examples for training, validation, and testing?
  \begin{itemize}
      Total: 5626 signatures (2913 original, 2713 forged)\\
      Train-validation-test split: 60-20-20 ratio
  \end{itemize}
\end{itemize}

\subsection{Machine Learning Algorithm}

Please describe the machine learning algorithm you want to use
for your project.

\noindent Please justify your selection.
    \begin{itemize}
        Siamese neural network. Siamese neural networks are well-suited for matching different instances of same signature.
  \end{itemize}
\subsection{Expected Outcomes}

What is your expected outcome for this project?
    \begin{itemize}
        A signature verification system for banking, legal and financial authentication. Potential use for fraud prevention.
    \end{itemize}

\subsection{References}
\begin{itemize}
      Koch, G., Zemel, R., Salakhutdinov, R. (2015). Siamese neural networks for one-shot image recognition. \textit{ICML deep learning workshop}, vol. 2. https://paperswithcode.com/paper/siamese-neural-networks-for-one-shot-image
  \end{itemize}

\end{document}
